Graph Generators for Data Science: A Survey

### 2018-07-02 generators_SocialNetworks.tex
Minor fixes

On-line social networks, like Facebook, Twitter, or LinkedIn, have become a
phenomenon used by billions of people every day and thus providing extremely
useful information for various domains. However, an analysis of such type of
graph has to cope with two problems: (1) availability of the data and (2)
privacy of the data. Hence, data generators which provide realistic synthetic
social network graphs are in great demand.

Analyses of social networks identify their various specific
features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, the social
graph has high \emph{clustering coefficient}, i.e. the degree of transitivity of
a graph. Or, its diameter, i.e. the minimum number of hops in which some
fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is
usually low due to weak ties joining faraway cliques. Another important aspect
of social networks is the community effect. A detailed study of structure of
communities in 70 real-world networks is provided, e.g., in
paper~\cite{Leskovec:2008:SPC:1367497.1367591}. Authors of
paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the structure of
communities (clustering coefficient, triangle participation ratio, bridges,
diameter, conductance and size) in both real graphs and output by existing graph
generators LFR~\cite{PhysRevE.78.046110} and the
LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. %They discover that communities
found among different graphs follow quite similar distributions and that
communities in a single graph have diverse nature, and are difficult to fit with
a single model.

Network generators can be categorized into statistical and agent-based.
\emph{Statistical
approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016}
focus on reproducing aspects of the network statistics. In \emph{agent-based
approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}
the networks are constructed by directly simulating the agents' social choices.

>>>>

On-line social networks, like Facebook, Twitter, or LinkedIn, have become a
phenomenon used by billions of people every day. Their bussiness model is
heavily based on understanding the behavior and interests of their users, and
thus their analysis has been proven to be of an inestimable value.  However,
doing research on novel and more efficient ways to analyze such requires the
access to real datasets, which is in most cases not possible since companies
holding the data do not want to or cannot share them. Hence, social network
generators which provide realistic synthetic outputs are in great demand.

Compared to other types of networks (e.g. computer networks or road networks),
social networks exhibit a set of particular characteristics as explained in
~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, people tend to
connect to persons with similar interests, persons geo-located closely, family
members or persons studying or working at the same place. This leads to the
formation of what are known as communities (modules of highly interconnected
persons that share similarities), which in turn makes these networks to exhibit
a large clustering coefficient (e.g. percentage of transitive relations or
triangles).  Such modular structure also leads to the formation of a network
with a small diameter, i.e. the minimum number of hops in which some fraction
(e.g., 90\%) of all connected pairs of nodes can reach each other. This is
usually due to weak ties connecting far away modules. Finally, social networks
usually have a large largest connected component, accounting for more than 90\%
of its nodes.

A detailed study of the structure of communities in 70 real-world networks is
provided, e.g., in paper~\cite{Leskovec:2008:SPC:1367497.1367591}. Additionally,
authors of paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the
structure of communities (clustering coefficient, triangle participation ratio,
bridges, diameter, conductance and size) in both real graphs and output by
existing graph generators LFR~\cite{PhysRevE.78.046110} and the
LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. They discover that communities
found among different graphs follow quite similar distributions and that
communities in a single graph have diverse nature, and are difficult to fit with
a single model.

Exhisting, social network generators try to reproduce different aspects of the
generated network, from high can be categorized into statistical and agent-based.
\emph{Statistical
approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016}
focus on reproducing aspects of the network statistics. In \emph{agent-based
approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}
the networks are constructed by directly simulating the agents' social choices.
